---
title: "linearModelWithPrediction" 
author: leia 
output: html_document
date: "2023-11-23"
---

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model1 

find an equation that expresses SIMS as a function of ARM 

## Results 

### Graphical results 

```{r}
plot(data$SIMS,data$ARM)
```

this graph shows as arm strength increases the sim score increases as well. there is a postive trend between arm strength 

### Numerical results 

```{r}
cor(data$SIMS, data$ARM)
```

we have a postive correlation, with noise(aka scatter). 



