---
title: "linearModelWithPrediction" 
author: leia 
output: html_document
date: "2023-11-23"
---

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model1 

find an equation that expresses SIMS as a function of ARM 

## Results 

### Graphical results 

```{r}
plot(data$SIMS,data$ARM)
```

this graph shows as arm strength increases the sim score increases as well. there is a postive trend between arm strength 

### Numerical results 

```{r}
cor(data$SIMS, data$ARM)
```

we have a postive correlation, with noise(aka scatter). 

### Inference 

```{r}
Model1 = lm(SIMS~ARM, data = data)
print(summary(Model1))
```

```{r}
plot(SIMS~ARM,data=data)
abline(Model1, col="blue")
```

the line in the data shows the best linear fit. for an increase of 1 in arm strength sim scire increases by 0.0545. 

```{r}
newdata = data.frame(ARM = 88, GRIP = 94)
predict.lm(Model1, newdata, interval="prediction")
```

## Model2 

find an eqaution that  expresses SIMS as a function of GRIP  

## Results 

### Greaphical Results 

```{r}
plot(SIMS~GRIP,data=data)
```

this graph shows a grip strength increases the sim score increases as well there is a possible trend between grip strength and sim score. 

### Numerical results 

```{r}
cor(data$SIMS, data$GRIP)
```

We have a postive correlation with noise (aka scatter) 

### Inference 

```{r}
Model2 = lm(SIMS~GRIP, data = data)
print(summary(Model2))
```

```{r}
plot(SIMS~GRIP,data=data)
abline(Model2, col="blue")
```

the line in the data shows the best linear fit. for an increase of 1 in arm strength sim scire increases by 0.0545. 
